Regenerate figures for the GMEA paper

### 2023-12-20 figs/main.Rmd
added main script

GSE158422.Rmd
GSE158422_simulate020.Rmd
GSE158422_simulate050.Rmd
GSE158422_simulate100.Rmd
GSE158422_simulate_summary.Rmd

@@

GSE158422_sensitivity.Rmd

@@

GSE158422_rna_int.Rmd

@@

aging_example.Rmd

@@

ART_estill2016.Rmd
ART_novakovic.Rmd
art_example.Rmd

>>>>

rmarkdown::render("GSE158422.Rmd")
rmarkdown::render("GSE158422_simulate020.Rmd")
rmarkdown::render("GSE158422_simulate050.Rmd")
rmarkdown::render("GSE158422_simulate100.Rmd")
rmarkdown::render("GSE158422_simulate_summary.Rmd")

@@

rmarkdown::render("GSE158422_sensitivity.Rmd")

@@

rmarkdown::render("GSE158422_rna_int.Rmd")

@@

rmarkdown::render("aging_example.Rmd")

@@

rmarkdown::render("ART_estill2016.Rmd")
rmarkdown::render("ART_novakovic.Rmd")
rmarkdown::render("art_example.Rmd")
